On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-12-02 paper/paper.tex
Improve a couple subsection titles
slight editing

A major benefit of the Haskell language is that it is frequently possible to
derive a Haskell implementation from a specification, either partially or fully.
In \cite{Bird:2010:Pearls} a collection of algorithms is presented with implementations derived in this
manner. The work \cite{Gibbons:2002:Calc} describes many of the
mathematical tools underlying such program derivations.
Recent examples of this technique include the work in
\cite{Elliott-2018-ad-icfp}, where an implementation of automatic
differentiation is derived from a specification
of derivatives.  Similarly, the work in
\cite{Elliott2019-convolution-extended} derives an implementation of a
generalized form of convolution from a specification.  When it is not possible to fully derive an implementation, it is often easier to check a Haskell implementation against a
specification than it is in many imperative languages due, in part, to the
management of side effects in Haskell. This is more difficult to do using an
imperative language such as C, as they provide no restrictions on where side
effects can occur.

@@

\subsection{\ttt{E (SumMatch a b)}}

@@

\subsection{\ttt{E (ProdMatch s t)}}

>>>>

A major benefit of the Haskell language is that it is frequently possible to
derive a Haskell implementation from a specification, either partially or fully.
In \cite{Bird:2010:Pearls}, a collection of algorithms is presented with implementations derived in this
manner. The work in \cite{Gibbons:2002:Calc} describes many of the
mathematical tools underlying such program derivations.
Recent examples of this technique include the work in
\cite{Elliott-2018-ad-icfp}, where an implementation of automatic
differentiation is derived from a specification
of derivatives.  Similarly, the work in
\cite{Elliott2019-convolution-extended} derives an implementation of a
generalized form of convolution from a specification.  When it is not possible to fully derive an implementation, it is often easier to check a Haskell implementation against a
specification than it is in many imperative languages due, in part, to the
management of side effects in Haskell. This is more difficult to do using an
imperative language such as C, as they provide no restrictions on where side
effects can occur.

@@

\subsection{Lists of branches}

@@

\subsection{Product matches}
